D3064R0: How to Avoid OOTA Without Really Trying

### 2024-02-17 ootavacuous.tex
More Alan Stern February 16 feedback
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

A drawback of the definition is that it is only relative to a specific
compiler or implementation.
This may strike some people as avoiding the real problem, in that a given
piece of code should either contain or not contain a semantic dependency
independent of the implementation used to run it.

>>>>

A drawback of the definition is that it is only relative to a specific
compiler or implementation.
This may strike some people as wishy-washy and as avoiding the real
problem, in that a given piece of code should either contain or not
contain a semantic dependency independent of the implementation used to
run it.
